\sysfull

### 2019-06-25 paper/TOSN/response-letter/responseLetter.tex

\response{These typos are corrected.}

\end{responses}

\begin{additionalQuestions}
\referee{Does this paper cite and use appropriate references?: No\\
If not, what important references are missing?: 
Ratchet and Clank were the first to propose using a timer for breaking up a long task so that it can make forward progress during short power cycles.  The authors propose the idea as if they were the first to use it.}

\response{Ratchet and Clank are mentioned and referenced in our original paper. 
In Section 4.2, we explicitly mentioned that the timer-based approach is similar to [72]; [72] references the ``Ratchet'' paper. 
In Section 9 we explained the core difference between our timer-based approach and the approach explained  in ``Ratchet'' paper. Furthermore, In Section 9 and Table 1 we mentioned Ratchet and Clank by names.}
\end{additionalQuestions}

### 2019-06-27 paper/TOSN/response-letter/responseLetter.tex

\referee{However, I was hoping to see more evaluations to understand the effect of capacitor size. In the introduction, authors state that "Coala is the only system that eliminates restructuring and re-compilation of applications considering device’s energy buffer". However, in the evaluation, I didn't find any graph related to the performance of Coala w.r.t to different capacitor sizes.}

\response{An additional experiment regarding the capacitor size has been conducted and the results are added to Section 8.2.}

\referee{I would have also liked to see a comparison between Coala and Region Formation [2]. Both try to reduce checkpointing overhead.}

\response{As it is indicated in response \hyperref[C:1]{[C:1]}, Coala addresses deficiencies in the \emph{static} task-based systems and provides a more efficient alternative. Therefore, we compared its performance against the performance of the state-of-the-art task-based runtime.}

### 2019-06-27 paper/TOSN/evaluation.tex
first revised version

\caption{\add{Comparison of \sys performance on two different capacitor sizes using the \textit{sort} application. We see that \sys optimizes its coalesced task size based on the energy buffer size.
\textbf{Coalesced task} refers to the first coalesced task after a reboot, \textbf{Exp. time} shows the experiment duration, the \textbf{Runs} column lists the number of complete runs of the application during the experiments. \textbf{Run time} is the device collective uptime needed to finish a single iteration of the \textit{sort} application.}
}
\label{tab:dif_cap}
\add{
\begin{minipage}{\columnwidth}
\begin{center}
\begin{tabular}{llllll}
  \toprule
    \textbf{Cap. size} ($\mu\text{f}$)& \textbf{Exp. time} ($s$)& \textbf{Duty cycle} & \textbf{Coalesced task} ($ms$)   & \textbf{Runs} & \textbf{Run time} ($ms$) \\
        \hline
    47                 &1205             & 12.93\%    & 33                        & 85       & 183      \\
    470                &1205             & 12.79\%    & 88                        & 87       & 177 \\
  \bottomrule
\end{tabular}
\end{center}
\end{minipage}  
}
\end{table}%

@@

\paragraph{Benefits of Adaptive Tasks.}
%
We now compare \sys's performance to Alpaca~\cite{alpaca}---a
\emph{non-adaptive} task-based system with tasks fixed at compile-time.
Fig.~\ref{fig:runtime} shows the average execution time of each
application for \sys and Alpaca, \add{normalized to the latter or, when not possible, to one second}.
\sys provides a performance benefit compared to Alpaca for most
applications. \add{For example, it is 54\% faster than Alpaca when executing the \textit{sort} application. In general,}  the speedup is greatest for applications with repeated WAR
dependencies throughout their code, particularly involving arrays
(\textit{dijkstra}, \textit{fft} and \textit{sort}). \sys's VMM
successfully amortizes the overhead of protecting memory that is accessed in
such patterns.  In applications without locality among accesses to protected
variables \sys incurs overhead from memory
virtualization that causes its performance to be comparable to (or worse than)
Alpaca (\textit{ar}, \textit{cuckoo}).

>>>>

\caption{\add{Comparison of \sys performance running the \textit{sort} application on two different capacitor sizes. We see that \sys optimizes its coalesced task size based on the energy buffer size.
\textbf{Coalesced task} refers to the first coalesced task after a reboot, \textbf{Exp. time} shows the experiment duration, the \textbf{Runs} column lists the number of complete runs of the application during the experiments. \textbf{Run time} is the device collective uptime needed to finish a single iteration of the \textit{sort} application.}
}
\label{tab:dif_cap}
\add{
\begin{minipage}{\columnwidth}
\begin{center}
\begin{tabular}{llllll}
  \toprule
    \textbf{Cap. size} ($\mu\text{f}$)& \textbf{Exp. time} ($s$)& \textbf{Duty cycle} & \textbf{Coalesced task} ($ms$)   & \textbf{Runs} & \textbf{Run time} ($ms$) \\
        \hline
    47                 &1205             & 12.93\%    & 33                        & 85       & 183      \\
    470                &1205             & 12.79\%    & 88                        & 87       & 177 \\
  \bottomrule
\end{tabular}
\end{center}
\end{minipage}  
}
\end{table}%

@@

\paragraph{Benefits of Adaptive Tasks.}
%
We now compare \sys's performance to Alpaca~\cite{alpaca}---a
\emph{non-adaptive} task-based system with tasks fixed at compile-time.
Fig.~\ref{fig:runtime} shows the average execution time of each
application for \sys and Alpaca, \add{normalized to the latter or, when not possible, to one second}.
\sys provides a performance benefit compared to Alpaca for most
applications. \add{For example, it is 54\% faster than Alpaca when executing the \textit{bc} application. In general,}  the speedup is greatest for applications with repeated WAR
dependencies throughout their code, particularly involving arrays
(\textit{dijkstra}, \textit{fft} and \textit{sort}). \sys's VMM
successfully amortizes the overhead of protecting memory that is accessed in
such patterns.  In applications without locality among accesses to protected
variables \sys incurs overhead from memory
virtualization that causes its performance to be comparable to (or worse than)
Alpaca (\textit{ar}, \textit{cuckoo}).
